Truthfulness Verification System

### 2011-02-23 trunk/proposal/paper.tex
final touch

\author{
Tathagata Dasgupta, ABM Musa\\
Email: \{tdasgu2, amusa2\}@uic.edu }

@@

\subsubsection{Use of Co-reference Program}
Totha: please write up two lines here

>>>>

\author{
Tathagata Dasgupta, ABM Musa\\
Email: \{tdasgu2, amusa2\}@uic.edu\\
URL: http://code.google.com/p/tverifier }

@@

\subsubsection{Use of Co-reference Program}
Coreference resolution is the process of determining whether two
expressions in natural language refer to the same entity in the world.
\cite{doi:10.1162/089120101753342653}.
In the context of previous example we can use co-reference resolution
if we have sentences like

\emph{"Tom Hanks is the lead actor in the movie Sleepless in Seatle.
He was nominated for the Golden Globe awards for this movie in 1994."
}

The pronoun "He" refers to Tom Hanks and would imply
the document is about a male, allowing us to disambiguate Tom Hank's
gender. The popular conference resolution api-s in use are those from
LingPipe\cite{LingPipecoref} and OpenNLP \cite{OpenNLPcoref}. We have
not yet evaluated them, and pondering if it would add sufficient value
to the system as the topic units need not be so specific. More
ontological information might already be available.
